### 2015-07-24 src/intro/intro.tex
Changes Pieter suggested.

For many actions, the brain needs to disentangle the contributions of gravity and linear acceleration to the gravito-intertial force. For example, the linear vestibulo-ocular reflex (LVOR) that stabilizes gaze during translation should be sensitive to translation while ignoring gravity. Under normal circumstances, the brain is able to perform this task well \cite{merfeld1995}, but during extreme conditions such as in airplanes or space flight errors might occur. The somatogravic illusion \cite{glasauer1995} is an example of a disambiguation error. In this illusion an airplane accelerates forward which causes an inertial force in the opposite direction. The direction of the resulting GIF will therefore be in between gravity (downward) and the intertial force (backward). The brain erroneously interprets the (majority of the) GIF as being caused by gravity, leading to the perception of "nose-up" pitch tilt.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\panelref{intro:fig:vection}{A}) for example causes a different pattern than roll rotation (\panelref{intro:fig:vection}{B}). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

    \caption{Vection pattern during \panel{A} lateral translation and \panel{B} rotation. During translation nearby targets (red) have a larger retinal displacement compared to far away ones (blue). Retinal displacement across rotation does not depend on target distance. }
    \label{intro:fig:vection}
\end{figure}

@@

\section{Vestibular reflexes for the self-motion compensation}
While vection is a valuable cue to self-motion perception, the brain wants to minimize vection because it blurs the image on the fovea, which hampers visual perception. Several reflexive mechanisms attempt to keep stable fixation to avoid image blurring during self-motion. Two such mechanisms are the vestibulo-ocular reflex, the VOR \cite{goldberg2012}, and the optokinetic reflex, the OKR \cite{purves2012}.

@@

In this equation, $P(x)$ represents the prior probability of the stimulus, that is the probability of the stimulus occurring without taking the sensory input into account. The left-hand side of the equation, $P(x|x_1,\dotsc,x_n$, is commonly referred to as the posterior probability.

>>>>

For many actions, the brain needs to disentangle the contributions of gravity and linear acceleration to the gravito-intertial force. For example, the linear vestibulo-ocular reflex (LVOR) that stabilizes gaze during translation should be sensitive to translation while ignoring gravity. Under normal circumstances, the brain is able to perform this task well \cite{merfeld1995}, but during extreme conditions such as in airplanes or space flight errors might occur. The somatogravic illusion \cite{glasauer1995} is an example of a disambiguation error. In this illusion an airplane accelerates forward which causes an inertial force in the opposite direction. The direction of the resulting GIF will therefore be in between gravity (downward) and the intertial force (backward). The brain erroneously interprets the (majority of the) GIF as being caused by gravity, leading to the perception of ``nose-up'' pitch tilt.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\panelref{intro:fig:vection}{A}) for example causes a different pattern than yaw rotation (\panelref{intro:fig:vection}{B}). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

    \caption{Vection pattern during \panel{A} lateral translation and \panel{B} rotation. During translation nearby targets (black) have a larger retinal displacement compared to far away ones (blue). Retinal displacement across yaw rotation does not depend on target distance. }
    \label{intro:fig:vection}
\end{figure}

@@

\section{Vestibular reflexes for self-motion compensation}
While vection is a valuable cue to self-motion perception, the brain wants to minimize vection because it blurs the image on the fovea, which hampers visual perception. Several reflexive mechanisms attempt to keep stable fixation to avoid image blurring during self-motion. Two such mechanisms are the vestibulo-ocular reflex, the VOR \cite{goldberg2012}, and the optokinetic reflex, the OKR \cite{purves2012}.

@@

In this equation, $P(x)$ represents the prior probability of the stimulus, that is the probability of the stimulus occurring without taking the sensory input into account. The left-hand side of the equation, $P(x|x_1,\dotsc,x_n$), is commonly referred to as the posterior probability.
